Testing Charts: viewer's perceptual accuracy in surveys

### 2023-06-19 SDSS-2023/testing-charts-accuracy.qmd
references

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
bibliography: "`r rbbt::bbt_write_bib('references.bib', overwrite = TRUE, library_id=rbbt::bbt_library_id('Graphics Research'))`"
abstract: "The use of visuals is a key component in scientific communication, and decisions about the design of a data visualization should be informed by what design elements best support the audience's ability to perceive and understand the components of the data visualization. We build on the foundations of Cleveland and McGill's work in graphical perception, employing a large, nationally-representative, probability-based panel of survey respondents to test perception in statistical charts. Our findings provide actionable guidance for data visualization practitioners to employ in their work."
keywords: 'list, keywords, here, 3-6, are, fine'
format: 
  pdf:
    include-in-header:
      - edits.tex
      - authors.tex
      # - refs.tex
    keep-tex: true
    # template: template.tex
documentclass: jds
---

@@

library(readxl)
library(lubridate)
library(patchwork)
```

@@

>>>>

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
bibliography: "`r rbbt::bbt_write_bib('references.bib', overwrite = TRUE, library_id=rbbt::bbt_library_id('Graphics Research'), translator='bibtex')`"
abstract: "The use of visuals is a key component in scientific communication, and decisions about the design of a data visualization should be informed by what design elements best support the audience's ability to perceive and understand the components of the data visualization. We build on the foundations of Cleveland and McGill's work in graphical perception, employing a large, nationally-representative, probability-based panel of survey respondents to test perception in statistical charts. Our findings provide actionable guidance for data visualization practitioners to employ in their work."
keywords: 'list, keywords, here, 3-6, are, fine'
format: 
  pdf:
    include-in-header:
      - edits.tex
      - authors.tex
      # - refs.tex
    keep-tex: true
    # template: template.tex
documentclass: jds
---

@@

library(readxl)
library(lubridate)
library(patchwork)
library(survey)
```

```{r data}
# other github repo. 
round1 <- readRDS("~/Documents/projects/NORC/visual-studies/data/round1.rds")
round2 <- readRDS("~/Documents/projects/NORC/visual-studies/data/round2.rds")

survey1 <- survey::svydesign(
  data = round1 %>% 
            filter(ab != "SKIPPED ON WEB", cd != "SKIPPED ON WEB"), 
  ids = round1$CaseId, weights = round1$weight)

survey2 <- survey::svydesign(
  data = round2 %>% 
            filter(ab != "SKIPPED ON WEB", cd != "SKIPPED ON WEB"), 
  ids = round2$CaseId, weights = round2$weight)

```

@@

```{r}
round_n1 <- nrow(round1)
round_n2 <- nrow(round2)
# effective sample size n/D, where D is the design effect
d1 <- deff(survey1)
```
All calculations in this paper are done in R [@R2022] using the `survey` package [@lumleyAnalysisComplexSurvey2004] version 4.0 [@survey] based on @lumleyComplexSurveysGuide2010.
